### 2019-11-25 discussion.tex
final tvcg

\section{Discussion and Conclusion}
\label{sec:discuss}
\saj{In this paper, we have introduced \noah, an in-situ navigation interface, designed as a spreadsheet plugin.
Using \noah, users can get a bird’s-eye view of the data, with the ability to scroll or seek
additional details on demand, using a multi-granularity overview, as well as
aggregate columns that eliminate cumbersome steering operations. Quantitatively, we find \noah to speed up navigation without compromising the accuracy of the tasks. Qualitatively, study participants identify it as positively impacting their experience while overviewing and navigating large datasets, and issuing formulae. 
However, participants identified unfamiliarity and lack of transparency of operations as some of the limitations of \noah. In this section, we discuss
how to address these limitations
and highlight other future enhancement opportunities for \noah.}

\stitle{Transparency and documentation.} \saj{Several operations in \noah 
are quite different from typical spreadsheet interactions, \eg zooming, bin customization. Moreover, participants found some of the terminologies quite different from typical spreadsheet terminologies (see Section~\ref{sec:rq2}). In addition, some participants complained about the lack of explanation surrounding the overview construction and aggregate column computation. In the future, these issues can be addressed by using more relatable terminologies and improved documentation.}

\stitle{Maintaining spreadsheet look and feel.}
\saj{In subsequent versions of \noah, we can further 
display the appropriate formula for each bin as users hover 
over the corresponding cell on the aggregate column. 
Moreover, participants ($N=5$) noted the fact that \noah currently 
does not support user defined formulae, another possible future enhancement. Bin customization in \noah is performed using a menu bar which adds an additional step. In Excel, the cell splitting and merging operations are direct and only requires a single click. Similar direct adjustment of data grouping strategies have been explored for visualization tools~\cite{sarvghad2018embedded} and can be introduced in a future version of \noah.}

\stitle{Binning for different data types.} \saj{The experience 
surrounding the construction
of the overview
can be further improved, specially for categorical data.
Currently, the bins of the overview
can be customized
only after the overview is constructed.
Providing the users
the capability to
select the representation
(similar to bin customization)
of the overview could have addressed this issue.
Understanding the impact of these
representation choices for the overview
can be an interesting future research.}

\stitle{Scope of overview-spreadsheet coordination.} 
\saj{Spreadsheet users may perform various edit operations, 
\eg updating values, adding/deleting rows/columns. 
However, \noah currently assumes the data to be read-only. 
In our next version, we can add support for
propagating the spreadsheet updates to the overview. 
Moreover, the charts displayed in an \emph{aggregate column} are non-interactive, 
\ie users cannot interact with the charts to visually look up relevant or 
interesting data points within the spreadsheet. 
In the future, we plan to extend \noah to support visual querying 
through the charts in an aggregate column, similar to multi-modal linked selections in Keshif~\cite{yalccin2018keshif}.}

\stitle{Enhancing the navigation experience.} \noah currently constructs the overview on a single attribute. We can add support for multi-attribute navigation (\eg explore the Airbnb data by city and neighborhood), and multi-level navigation (\eg explore the neighborhoods after zooming into a specific city in the Airbnb data). Furthermore, bin customization currently supports changing the bin boundaries only while maintaining the current order. Supporting user defined ordering to allow arbitrary reshuffling of the bins can be another enhancement.\toappendix{ However, such modification will require a redesign of the histogram based data structure since the ordering property will not hold anymore.Finally, a complete characterization of the spreadsheet operations that can be supported by \noah is another open question, for example, other operations that involve working with subsets of spreadsheet data, \eg sorting, filtering, copy-pasting, can also be supported by \noah.}

\stitle{Expanding the scope of supported operations.} \saj{Spreadsheet operations that involve working with subsets of spreadsheet data, \eg sorting, filtering, copy-pasting, can also be supported by \noah. Therefore, it is necessary to  completely characterize the scope of spreadsheet operations that can be supported by \noah. Other enhancement includes adding annotations, \eg visual cues, texts, to the overview and then exporting the customized overview---a required feature for information seeking tools~\cite{shneiderman2003eyes}.}

\stitle{Beyond Tabular Data.} \noah operates only on tabular data.
However, spreadsheets can be semi-structured---formulae 
and text can be interspersed with tabular data. 
We can extend \noah to act as a map highlighting heterogeneous regions on such complex spreadsheets which users can utilize to navigate the spreadsheet. 
We can leverage existing work on spreadsheet table detection~\cite{tablesense}, 
and property identification~\cite{chen2017spreadsheet} 
to construct the map.

\stitle{From Perceptual to Interactive Scalability.} 
The current version of \noah addresses the perceptual 
scalability challenges while navigating 
Excel-scale (one million rows) data. 
As modern spreadsheets continue to support 
increasingly larger datasets---{\scshape DataSpread}~\cite{datamodels} 
supports one billion rows---the interactions proposed in this paper may violate the interactive response time bound of 500 ms~\cite{liu2014effects}. This opens the door to a new set of research challenges that may range from approximate query processing to progressive data analytics.

\noah represents our 
first step towards a general purpose spreadsheet navigation plug-in that can make spreadsheets more effective
on large datasets that are increasingly the norm.

>>>>

%!TEX root = main.tex
\section{Discussion and Conclusion}
\label{sec:discuss}
\new{\noah represents our 
first step towards a general purpose spreadsheet navigation plug-in to make spreadsheets more effective
when exploring datasets that are increasingly the norm. 
Using \noah, users can get a bird's eye view of the data, with the ability to scroll or seek
additional details on demand via a multi-granularity overview, as well as employ
aggregattion in-situ, which eliminates cumbersome steering operations. Quantitatively, we find that \noah speeds up navigation without compromising accuracy. Qualitatively, study participants identify it as positively impacting their experience while overviewing and navigating large datasets, and issuing formulae. However, the user study revealed some limitations of \noah. Moreover, the study design itself had some limitations. In this section, we discuss these limitations and propose extensions to address these limitations as well as enhance the capabilities of \noah.}

\subsection{User Study Limitations}
Our study has a few limitations that can be strengthened by future larger-scale and finer-grained studies.

\stitle{\new{Insufficient coverage of participant demographics.}} \new{Our participant pool demographics only partially represents the demographics of the general audience intended for \noah. A larger sample with more  participants with a range of skill-sets and backgrounds that better represents the spreadsheet user population would have provided more ecological validity to generalize our findings.}
%While a larger sample with more diverse backgrounds would have allowed us to perform more definitive quantitative analysis, we combined this analysis with qualitative survey, interview, and screen/audio recording data to provide insights that can be explained with multiple information sources.

\stitle{\new{Lack of targeted comparisons with advanced spreadsheet features.}} \new{We only compared the performance of a \noah-integrated spreadsheet with a traditional spreadsheet. We did not evaluate specific spreadsheet features like pivot table and \code{SUBTOTAL} as they violate most of the design considerations proposed in Section~\ref{sec:design}; we discussed their limitations in Section~\ref{sec:related}. We instead allowed the participants to freely use any spreadsheet operations that they were comfortable with (including the advanced ones), enabling us to observe how introducing a plug-in like \noah affected their navigation experience. However, a future study targeted at evaluating the pros and cons of these features for spreadsheet navigation would be valuable.}

\stitle{\new{Isolated evaluation of \noah components.}} \new{While we did present the impact of various components of \noah in Section~\ref{sec:rq2}, we did not isolate the effects of individual features during our study. For example, we did not study the effects of the binned overview (visual clarity versus visual continuity), display layout (screen space trade-off), and
contextual presentation of data (raw text versus chart representation of aggregate columns) in isolation. A more fine-grained study that teases apart the contribution of individual components of \noah is warranted.}

\subsection{Limitations of \noah and Possible Enhancements}
While we alluded to some limitations of \noah in Section~\ref{sec:results}, we now discuss these in more detail and how we can possibly overcome them.

\stitle{\new{Lack of transparency and documentation of new interactions.}} \new{Several operations in \noah 
are quite different from typical spreadsheet interactions, \eg zooming or bin customization. Moreover, participants found some of the terminologies, \eg explore or bin, to be rather different from typical spreadsheet terminologies, which took some getting used to (see Section~\ref{sec:rq2}). In addition, some participants complained about the lack of explanation surrounding the overview construction and aggregate column computation. In the future, these issues can be addressed by using more relatable terminologies and improved documentation.}

\stitle{\new{Deviation from the spreadsheet look and feel.}}
\new{A couple of participants ($P2$ and $P11$) mentioned that the aggregate column results hides the actual spreadsheet formula and they would prefer some visual cues that highlight the corresponding formula underlying each bin. Subsequent versions of \noah can  
display the appropriate formula for each bin as users hover
over the corresponding cell on the aggregate column\cut{making the output more relatable to typical spreadsheet formula results}. The aggregate column feature can be further enhanced by enabling users to issue user defined formulae, a feature requested by a number of participants ($N=5$). Another feature that can be made more similar to spreadsheet interaction semantics is the bin customization operation. Currently, this operation in \noah is performed from a menu bar, adding an additional step. The bin splitting and merging operations can be made more similar to how spreadsheet cells are split or merged---in Excel, these operations are direct and only require a single click. Similar direct adjustment of data grouping strategies have been explored for visualization tools~\cite{sarvghad2018embedded} and can be adapted to this setting.}

\stitle{\new{Absence of bespoke overview representations for various data types.}} \new{The experience 
surrounding the construction
of the overview
can be further improved, especially for categorical data.
Currently, the bins of the overview
can be customized
only after the overview is constructed.
Providing the users
the ability to
select the representation
(similar to bin customization)
of the overview at the outset could have possibly addressed this issue.
Understanding the impact of these
representation choices for the overview
is an interesting open question.}

\subsection{Additional enhancements}
We now discuss other functionalities that can be introduced to further enhance the capabilities of \noah.

\stitle{\new{Broadening the scope of overview-spreadsheet coordination.}} 
\new{Spreadsheet users often perform various edit operations, 
\eg updating values, adding/deleting rows/columns. 
However, our current \noah implementation assumes the data to be read-only. 
In our next version, we can add support for
propagating spreadsheet updates to the overview. 
Moreover, the charts displayed in an \emph{aggregate column} are non-interactive, 
\ie users cannot interact with the charts to visually look up relevant or 
interesting data points within the spreadsheet. 
In the future, we plan to extend \noah to support visual querying 
through the charts in an aggregate column, similar to multi-modal linked selections in Keshif~\cite{yalccin2018keshif}.}

\stitle{\new{Enabling more flexible overview binning.}} \noah currently constructs the overview on a single attribute. We can add support for multi-attribute navigation (\eg explore the Airbnb data by city and neighborhood), and multi-level navigation (\eg explore the neighborhoods after zooming into a specific city in the Airbnb data). Furthermore, bin customization currently supports changing the bin boundaries only, while maintaining the current order. Supporting user-defined ordering to allow arbitrary reshuffling of the bins can be another enhancement.\toappendix{ However, such modification will require a redesign of the histogram based data structure since the ordering property will not hold anymore.Finally, a complete characterization of the spreadsheet operations that can be supported by \noah is another open question, for example, other operations that involve working with subsets of spreadsheet data, \eg sorting, filtering, copy-pasting, can also be supported by \noah.}

\stitle{\new{Supporting other spreadsheet operations.}} \new{Spreadsheet operations that involve working with subsets of the data, \eg sorting, filtering, copy-pasting, can be supported by \noah, but our current implementation does not support them. Future versions would support such operations as well. Other enhancements include adding annotations, \eg visual cues, text, to the overview and then exporting the customized overview for presentation or reporting---a required feature for information seeking tools~\cite{shneiderman2003eyes}.}

\stitle{\new{Supporting navigation for semi-structured data.}} \noah operates only on tabular data.
However, spreadsheets can be semi-structured---formulae 
and text can be interspersed with tabular data. 
\new{In such cases, NOAH can be used to support exploration and zooming for each such tabular region independently, supported by an overall overview (akin to a map-based panning tool) for users to select which tabular region they want to explore in detail.}
We can leverage existing work on spreadsheet table detection~\cite{tablesense}, 
and property identification~\cite{chen2017spreadsheet} 
to \new{support such extensions}.

\stitle{\new{Achieving interactive scalability beyond traditional spreadsheet limits.}} 
The current version of \noah addresses the perceptual 
scalability challenges while navigating 
Excel-scale (one million rows) data. 
As modern spreadsheets continue to support 
increasingly larger datasets---{\scshape DataSpread}~\cite{datamodels} 
supports one billion rows---the interactions proposed in this paper may violate the interactive response time bound of 500 ms~\cite{liu2014effects}. This opens the door to a new set of research challenges that may range from approximate query processing to progressive data analytics.

### 2019-11-25 introduction.tex
final tvcg

\stitle{\noah: \new{a navigation plug-in for spreadsheets}.} We address the aforementioned challenges
in \noah,
an in-situ
\textbf{\underline{n}}avigation interface
for \textbf{\underline{o}}verviewing
and \textbf{\underline{a}}nalyzing
spreadsheet data \textbf{\underline{h}}olistically.
\noah is constructed as a plugin to
an existing spreadsheet tool,
{\scshape DataSpread}~\cite{dataspread},
an open-source scalable web-based spreadsheet.
While \noah's design is not tied to {\sc DataSpread},
we opted not to use other popular spreadsheet
tools like Google Sheets and Microsoft Excel because they
are closed source.
Figure~\ref{fig:ux} shows a snapshot of \noah.
When the user chooses to explore
the data by a specific attribute,
\new{a multi-granularity overview is constructed and displayed
within \noah, next to the raw spreadsheet data (Figure~\ref{fig:ux}a). Users can zoom into or out of the overview to obtain a fine or coarse-grained 
perspective of the data distribution. 
The distribution at each granularity 
is captured by a histogram,
enabling users to assimilate the data \new{via summary
statistics}. 
Each bin (group) of the histogram is 
mapped to a collection of rows in the spreadsheet.} 
Cumbersome scrolling operations are eliminated in favor
of a few clicks on the overview interface. Instead of steering to analyze the data,
users can issue formulae
on the overview with interactions similar to pivot table construction,
and view results on a separate {\em aggregate column},
alongside the overview (Figure~\ref{fig:ux}b). 
In this manner,
users can issue formulae on different
subsets of the data while remaining on the same screen,
reducing visual discontinuity.
\noah ensures that there is coordination between
the overview and the spreadsheet:
for example, panning and zooming on the overview
are reflected on the spreadsheet by displaying
the spreadsheet data corresponding to the bin
currently in focus in the overview.
Finally, \noah automatically creates
contextual and historical information
(Figure~\ref{fig:ux}d and~\ref{fig:ux}e)
while displaying visual cues
(Figure~\ref{fig:ux}f and~\ref{fig:ux}g)
so that users don't lose context during navigation.

>>>>

\stitle{\noah: \new{a navigation plug-in for spreadsheets}.} We address the aforementioned challenges
in \noah\footnote{\new{A video demo of \noah can be found at https://www.youtube.com/watch?v=iZsboe3x680}},
an in-situ
\textbf{\underline{n}}avigation interface
for \textbf{\underline{o}}verviewing
and \textbf{\underline{a}}nalyzing
spreadsheet data \textbf{\underline{h}}olistically.
\noah is constructed as a plugin to
an existing spreadsheet tool,
{\scshape DataSpread}~\cite{dataspread},
an open-source scalable web-based spreadsheet.
While \noah's design is not tied to {\sc DataSpread},
we opted not to use other popular spreadsheet
tools like Google Sheets and Microsoft Excel because they
are closed source.
Figure~\ref{fig:ux} shows a snapshot of \noah.
When the user chooses to explore
the data by a specific attribute,
\new{a multi-granularity overview is constructed and displayed
within \noah, next to the raw spreadsheet data (Figure~\ref{fig:ux}a). Users can zoom into or out of the overview to obtain a fine or coarse-grained 
perspective of the data distribution. 
The distribution at each granularity 
is captured by a histogram,
enabling users to assimilate the data \new{via summary
statistics}. 
Each bin (group) of the histogram is 
mapped to a collection of rows in the spreadsheet.} 
Cumbersome scrolling operations are eliminated in favor
of a few clicks on the overview interface. Instead of steering to analyze the data,
users can issue formulae
on the overview with interactions similar to pivot table construction,
and view results on a separate {\em aggregate column},
alongside the overview (Figure~\ref{fig:ux}b). 
In this manner,
users can issue formulae on different
subsets of the data while remaining on the same screen,
reducing visual discontinuity.
\noah ensures that there is coordination between
the overview and the spreadsheet:
for example, panning and zooming on the overview
are reflected on the spreadsheet by displaying
the spreadsheet data corresponding to the bin
currently in focus in the overview.
Finally, \noah automatically creates
contextual and historical information
(Figure~\ref{fig:ux}d and~\ref{fig:ux}e)
while displaying visual cues
(Figure~\ref{fig:ux}f and~\ref{fig:ux}g)
so that users don't lose context during navigation.

### 2019-11-25 letter.tex
final tvcg

A previous version of this paper was submitted to InfoVis 2019. This version was rejected as the paper co-chairs deemed that revising the paper would require more time than allocated to meet reviewer expectations. The paper co-chairs mentioned the following: ``\textit{We particularly encourage such revisions where submissions were positively received by reviewers, but the revisions required were deemed to be beyond the scope of the conference review cycle. If you address the issues raised and subsequently submit to TVCG, please make reference to this  InfoVis submission and include a description of how you addressed the InfoVis reviewers' comments.}'' The entire set of reviews are attached. In particular, the reviewers asked for the following changes for a revision: 

@@

Every section in the paper has been revised;
the changes are highlighted in \new{blue}.

@@

we opted for histograms as an overview representation, \new{by contextualizing our
approach using prior work on multi-scale aggregation~\cite{elmqvist2009hierarchical}.} 

@@

for the quiz tasks and discuss 
three limitations of our study in detail. 

@@

\item In Section~\ref{sec:discuss}, we have added a summary of our takeaways from the evaluation study, while discussing additional limitations of \noah and future enhancement opportunities. 

@@

\item \textit{Merits over other tools} (\textbf{C1}): 
Throughout the paper (and especially in 
Sections~\ref{sec:intro}, \ref{sec:related},
and \ref{sec:study}), we have emphasized
that the main contribution of \noah
is its \emph{design as a general-purpose navigation plug-in} 
to any existing spreadsheet system. 
As spreadsheets have a massive user-base, 
enhancing exploration and formula computation 
on large datasets while maintaining 
the spreadsheet look-and-feel as much as possible, 
has the potential to impact hundreds of millions 
of spreadsheet users. 
Most of these users employ spreadsheets 
as their primary data management and analysis 
tool while shunning enterprise solutions 
with more advanced features. 
Therefore, our goal is to develop a 
solution to improve navigation within spreadsheets.
Indeed, we could have tried to enhance navigation
in other tools, such as Keshif, or Tableau, like
the reviewers suggest---but we would be forcing
spreadsheet users to adopt an entirely new tool, something
that they are clearly loath to do.

@@

\item \textit{Justification of Excel as a Baseline} (\textbf{C3}):
Since our goal is to improve spreadsheet
user experience---and there are very good reasons for doing so,
as outlined in item 1) above---the natural comparison point
is Excel. 
That said, beyond popularity, 
we have provided a thorough justification
for what spreadsheet systems like Excel offer
relative to tabular data analysis tools (TDA),
making it a more appropriate point of comparison.
Our justification for using Excel over 
tabular data analysis (TDA) tools involves 
a) highlighting the appeal of spreadsheets 
among users who shun more advanced enterprise 
tools (Section~\ref{sec:intro}), 
b) identifying the scope of tasks 
supported by spreadsheets and 
TDA tools (Section~\ref{sec:usage} and~\ref{sec:related}), 
c) explaining that the goal of spreadsheets 
is to present the raw data as is, 
amenable to editing, formula computation, 
and comparison of derived data, all done in-situ,
unlike TDA tools that hide the data 
while providing summarized statistics 
(Section~\ref{sec:related}), and 
d) highlighting the importance of 
addressing the shortcomings of a tool, 
the user base of which far exceeds 
that of TDA tools (Section~\ref{sec:study}).

@@

\item \textit{Reporting Intra-participant Differences} (\textbf{C6}):
\newsaj{We performed additional analysis of the study data to report intra-participant submission time differences for the quiz phase tasks. While we summarize the results of the analysis in Section~\ref{sec:time_acc}, the detailed result can be found in Appendix}\agp{pls add; insights on trends sounds vague let's be more clear}. \newsaj{We find that, despite a few exceptions, across all tasks, participants' task submission times were faster using \noah---all but one participants completed at least four tasks in less time using \noah compared to Excel.} However, we already obtained similar observations from Figure~\ref{fig:timeBox} in Section~\ref{sec:rq1}. Therefore, we have included the results of the intra-participant analysis in Appendix.
\end{enumerate}

>>>>

A previous version of this paper was submitted to InfoVis 2019 (submission ID: 1043). This version was rejected as the paper co-chairs deemed that revising the paper would require more time than allocated to meet reviewer expectations. The paper co-chairs mentioned the following: ``\textit{We particularly encourage such revisions where submissions were positively received by reviewers, but the revisions required were deemed to be beyond the scope of the conference review cycle. If you address the issues raised and subsequently submit to TVCG, please make reference to this InfoVis submission and include a description of how you addressed the InfoVis reviewers' comments.}'' The entire set of reviews and the old INFOVIS submission are attached  at the end of this document. The reviewers asked for the following changes for a revision: 

@@

Every section in the paper has been revised. We have attached the new version of the paper with this ``summary of changes'' document, where
the changes are highlighted in \new{blue} for reviewers' convenience.

@@

we opted for histograms as an overview representation, by contextualizing our
approach using prior work on multi-scale aggregation~\cite{elmqvist2009hierarchical}. 

@@

for the quiz tasks in detail. 

@@

\item In Section~\ref{sec:discuss}, we have added a summary of our takeaways from the evaluation study, while discussing limitations of our evaluation study and \noah's design while highlighting future enhancement opportunities. 

@@

\item \textit{Merits over other tools} (\textbf{C1}): 
Throughout the paper (and especially in 
Sections~\ref{sec:intro}, \ref{sec:related},
and \ref{sec:study}), we have emphasized
that the main contribution of \noah
is its \emph{design as a general-purpose navigation plug-in} 
to any existing spreadsheet tool. 
As spreadsheets have a massive user-base, 
enhancing exploration and formula computation 
on large datasets while maintaining 
the spreadsheet look-and-feel as much as possible, 
has the potential to impact hundreds of millions 
of spreadsheet users. 
Most of these users employ spreadsheets 
as their primary data management and analysis 
tool while shunning enterprise solutions 
with more advanced features. 
Therefore, our goal is to develop a 
solution to improve navigation within spreadsheets.
Indeed, we could have tried to enhance navigation
in other tools, such as Keshif, or Tableau, like
the reviewers suggest---but we would be forcing
spreadsheet users to adopt an entirely new tool, something
that they are clearly loath to do.

@@

\item \textit{Justification of Excel as a Baseline} (\textbf{C3}):
Since our goal is to improve spreadsheet
user experience---and there are very good reasons for doing so,
as outlined in item 1) above---the natural comparison point
is Excel. 
That said, beyond popularity, 
we have provided a thorough justification
for what spreadsheet tools like Excel offer
relative to tabular data analysis tools (TDA),
making it a more appropriate point of comparison.
Our justification for using Excel over 
tabular data analysis (TDA) tools involves 
a) highlighting the appeal of spreadsheets 
among users who shun more advanced enterprise 
tools (Section~\ref{sec:intro}), 
b) identifying the scope of tasks 
supported by spreadsheets and 
TDA tools (Section~\ref{sec:usage} and~\ref{sec:related}), 
c) explaining that the goal of spreadsheets 
is to present the raw data as is, 
amenable to editing, formula computation, 
and comparison of derived data, all done in-situ,
unlike TDA tools that hide the data 
while providing summarized statistics 
(Section~\ref{sec:related}), and 
d) highlighting the importance of 
addressing the shortcomings of a tool, 
the user base of which far exceeds 
that of TDA tools (Section~\ref{sec:study}).

@@

\item \textit{Reporting Intra-participant Differences} (\textbf{C6}):
We performed additional analysis of the study data to report intra-participant submission time differences for the quiz phase tasks. While we summarize the results of the analysis in Section~\ref{sec:time_acc}, the detailed results can be found in Appendix. We find that despite a few exceptions, across all tasks, participants' task submission times were faster using \noah---all but one participants completed at least four tasks in less time using \noah compared to Excel. However, we already obtained similar observations from Figure~\ref{fig:timeBox} in Section~\ref{sec:rq1}. Therefore, we decided to include the results of the intra-participant analysis in the Appendix as opposed to the main paper.
\end{enumerate}

We realize that these extensive changes throughout the paper have increased the paper length. As the TVCG submission guidelines indicate ``\emph{The regular paper page length limit is defined at 12 formatted
pages, including references and author biographies. Any pages or
fraction thereof exceeding this limit are charged \textdollar220 per page. Regular
papers may not exceed 18 formatted pages}'', so we have decided to let the paper length stand since our paper is at 16 pages currently — and we would be happy to pay for the extra pages. We would also be happy to reduce length by moving appropriate content from the main body to the supplementary material as suggested by reviewers. The following are attached with the ``Summary of changes'' document:
\begin{itemize}
    \item The resubmitted TVCG paper with changes highlighted in \new{blue}.
    \item The entire set of reviews of the INFOVIS submission.
    \item The previous INFOVIS submission.
\end{itemize}
